---
output: github_document
always_allow_html: true
---
# blast_graph

The purpose of the blast_graph function is to easily create a graph displaying the species in your BLAST+ output file.

```{r blast_graph_example, warning=FALSE}
library(funkyfigs)
blast_graph("data/sample_example.txt", 10)
```

# spectophotography_boxplot

The spectrophoto_boxplot function makes it easier to quickly generate a boxplot on your spectrophotography data.
Note: for the example, no actual spectophotography data was used. It's just an example of what the output should look like.

```{r spectrophoto_boxplot}
library(funkyfigs)
spectrophoto_boxplot(iris, iris$Species, iris$Sepal.Length)
```

# spectrophoto_bar

The spectrophoto_bar function easily gives an overview of your spectrophotography measurements, per group.
Note: for the example, no actual spectophotography data was used. It's just an example of what the output should look like.

```{r spectrophoto_bar_example}
library(funkyfigs)
spectrophoto_bar(iris, iris$Species, iris$Sepal.Length)
```

# url_table

Want to add some urls to your dataset, but it's too much of a hassle to put it per cell? url_table easily adds a column with the desired urls, per cell!

```{r url_table_example}
library(funkyfigs)
url_table(iris, iris$Species, urls = c(rep(c("https://en.wikipedia.org/wiki/Iris_setosa"), times = 50), rep(c("https://en.wikipedia.org/wiki/Iris_versicolor"), times = 50), rep(c("https://en.wikipedia.org/wiki/Iris_virginica"), times = 50)))
```
